Pteropod physiological analysis

### 2018-08-24 figures.Rmd
figs 6 and 7 legend as discrete

    }),
    plos = pmap(list(pldat, xvar, legr), function(pldat, xvar, legr){

@@

@@

      p1 <- ggplot() +
        geom_ribbon(data = pl1, aes_string(x = nms[3], ymin = 'lo', ymax = 'hi', group = nms[4]), alpha = 0.5, fill = 'grey') +
        geom_line(data = pl1, aes_string(x = nms[3], y = nms[1], group = nms[4], colour = nms[4]), size = 1) + 
        geom_text(data = pl2, aes(x= x, y = y, label = lab), hjust = 0) +
        theme_bw() +
        xlab(parse(text = xvar)) +
        scale_colour_gradientn(parse(text = legr), colours = cols) +
        scale_y_continuous(nms[1])

@@

    }),
    plos = pmap(list(pldat, xvar, yvar, legr, hjs), function(pldat, xvar, yvar, legr, hjs){

@@

      p1 <- ggplot() +
        geom_ribbon(data = pl1, aes_string(x = nms[3], ymin = 'lo', ymax = 'hi', group = nms[4]), alpha = 0.5, fill = 'grey') +
        geom_line(data = pl1, aes_string(x = nms[3], y = nms[1], group = nms[4], colour = nms[4]), size = 1) + 
        geom_text(data = pl2, aes(x= x, y = y, label = lab), hjust = hjs) +
        theme_bw() +
        xlab(parse(text = xvar)) +
        scale_colour_gradientn(parse(text = legr), colours = cols) +
        scale_y_continuous(yvar)

>>>>

    }),
    plos = pmap(list(pldat, xvar, cvar, legr), function(pldat, xvar, cvar, legr){

@@

      # leg vals as factor 
      pl1[[cvar]] <- factor(pl1[[cvar]], 
                            levels = sort(unique(pl1[[cvar]]), decreasing = T),
                            labels = round(sort(unique(pl1[[cvar]]), decreasing = T), 1)
      )

@@

      p1 <- ggplot() +
        geom_ribbon(data = pl1, aes_string(x = nms[3], ymin = 'lo', ymax = 'hi', group = nms[4]), alpha = 0.5, fill = 'grey') +
        geom_line(data = pl1, aes_string(x = nms[3], y = nms[1], group = nms[4], colour = nms[4]), size = 1) + 
        geom_text(data = pl2, aes(x= x, y = y, label = lab), hjust = 0) +
        theme_bw() +
        xlab(parse(text = xvar)) +
        scale_colour_manual(parse(text = legr), values = c(rev(cols)[1], cols[1])) +
        scale_y_continuous(nms[1])

@@

    }),
    plos = pmap(list(pldat, xvar, yvar, cvar, legr, hjs), function(pldat, xvar, yvar, cvar, legr, hjs){

@@

      p1 <- ggplot() +
        geom_ribbon(data = pl1, aes_string(x = nms[3], ymin = 'lo', ymax = 'hi', group = nms[4]), alpha = 0.5, fill = 'grey') +
        geom_line(data = pl1, aes_string(x = nms[3], y = nms[1], group = nms[4], colour = nms[4]), size = 1) + 
        geom_text(data = pl2, aes(x= x, y = y, label = lab), hjust = hjs) +
        theme_bw() +
        xlab(parse(text = xvar)) +
        scale_colour_manual(parse(text = legr), values = c(rev(cols)[1], cols[1])) +
        scale_y_continuous(yvar)
